\chapter*{General conclusion}
\addcontentsline{toc}{chapter}{General conclusion}
The following report narrates the work accomplished during my final study internship at “Appaxis innovations” in the process of doing the national diploma in software engineering.
During my internship I was able to demonstrate all the knowledge and skills which have been introduced at the ESPRIT learning process and build the “Uni-world” application. This application has been designed with the objectives of overcoming and enhancing the student lives by providing the students with an environment to fund their network  and where they get the transportation benefits.
We start with the short brief, based on which we presented initial analysis of our work, demonstrating the general setting of our project, the issue we try to address, and the solution we offer. We then continued and explained the requirements analysis as well as Scrum management. We then elaborated the realization of the release 1, 2 and 3 explaining the functionality of the Sprints involved.
This project help me to enhance my technical skills, discover new technologies and work with tools like Kotlin, jetpack compose, and node .js .
I also learnt how to accurately determine the time needed by a certain task in a project to be completed.
I also succeeded in learning about and applying the Scrum methodology during the development phase and to be a part of forming a company’s growth as a leader and and as a member of a very hardworking and talented team. \\

Finally, in addition to the improvements suggested by our users, we are considering the integration of certain features such as :
\begin{enumerate}
    \item  Real-time account verification process.
    \item Home-sharing functionalities.
    \item Appointment scheduling function that include : selection of date and selection of place with maps.
    \item Community and discussion group creation
    \item Events creation

\end{enumerate}